---
title: "Weather Information Preferences"
subtitle: "Summary Report for the `r params$region` Region"
author: "Author:  F. T .M. McKay"
date: "`r format(Sys.Date(),'%A, %B %d, %Y')`"
output: 
  ioslides_presentation:
    logo:  c:/RepTemplates/Module5_project1/images/sunstar.png
params:
  region: 
    label: "Region:"
    value: Mountain
    input: select
    choices: ["East North Central","East South Central", 
              "Middle Atlantic","Mountain", "New England", 
              "Pacific","South Atlantic", "West North Central",
              "West South Central"]
---

```{r, echo=FALSE, message=FALSE, warning=FALSE }
knitr::read_chunk("c:/RepTemplates/Module5_project1/code/setup.R")
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE }
```

```{r loadData}
```

 ```{r child="c:/RepTemplates/Module5_project1/text/backgroundSection.Rmd"}
```

```{r child="c:/RepTemplates/Module5_project1/text/purposeSection.Rmd"}
```

## _OPTIONAL_ Demographics of Survey Respondents in a Merged Table

This section is provided as an example of how to merge the three demographic summary tables for the `r nrow(sdat)` survey respondents above into a single merged table.

```{r makeTable, code=readLines("c:/RepTemplates/Module5_project1/code/makeTable.R")}
```

## Weather Source Preference by Gender

Finally, here is a breakdown of the `r nrow(sdat)` survey respondents for the `r params$region` region of the US on how they check their daily weather by gender.

```{r}
knitr::read_chunk("c:/RepTemplates/Module5_project1/code/makeChart.R")
```

```{r makeCharts}
```

The text sections and R code chunks have been updated with the region substitutions as needed for this lesson.